\section{Talks and Presentations}
\cvline{11/2022}
  {\strongHighlight{Invited Talk}:
    \emph{Modern DSL Compiler Development with MLIR},
    \small Huawei TRC Innovation Summit 2022, Tel Aviv, Israel.}
\cvline{06/2022}
  {\strongHighlight{Invited Talk}:
    \emph{How to Design the Next 700 Optimizing Compilers},
    \small High-efficiency computer graphics group at \strongHighlight{MIT CSAIL}, US.}
\cvline{06/2022}
  {Talk: \emph{Achieving High-Performance the Functional Way: Expressing High-Performanace Optimisations as Rewrite Strategies},
    \small SIGPLAN Track at the SIGPLAN Conference on Programming Language Design and Implementation (PLDI), US.}
\cvline{06/2022}
  {\strongHighlight{Invited Talk}:
    \emph{RISE \& Shine: Language-Oriented Compiler Design},
    \small Compiler Design Lab Seminar, Saarland University, Germany.}
\cvline{04/2022}
  {Talk: \emph{Systematically Extending a High-Level Code Generator with Support for Tensor Cores},
   \small Workshop on General Purpose Processing using GPU (GPGPU).}
\cvline{09/2021}
  {Talk: \emph{FHPNC Community Update},
   \small Workshop on Functional High-Performance and Numerical Computing (FHPNC).}
\cvline{08/2020}
  {Invited Lectures: \emph{Compiler Intermediate Representations},
  \small Scottish Programming Language and Verification Summer School,
  Hosted by the University of Edinburgh, UK.}
\cvline{06/2020}
  {Talk: \emph{Achieving High-Performance the Functional Way — Expressing High-Performance Optimizations as Rewrite Strategies},
  \small Scottish Programming Languages Seminar,
  Hosted by the University of Sterling, UK.}
\cvline{09/2019}
  {\strongHighlight{Invited Talk}: \emph{ ELEVATE: a language to write composable program optimizations},
  \small \strongHighlight{Google DeepMind}, London, UK.}
\cvline{02/2019}
  {\strongHighlight{Invited Talk}: \emph{Lift: Generating High Performance Code with Rewrite Rules},
  \small Programming Languages and Software Engineering Group, \strongHighlight{University of Washington in Seattle}, US.}
\cvline{02/2019}
  {\strongHighlight{Invited Talk}: \emph{Lift: Generating High Performance Code with Rewrite Rules},
    \small \strongHighlight{Microsoft Research in Redmond}, US.}
\cvline{12/2018}
         {Talk: \emph{Implementing lambda calculus in Python and C++},
          \small Programming Languages at Glasgow (PLUG), University of Glasgow, UK.}
\cvline{11/2018}
         {Talk: \emph{High-level Features – Low-level Performance: GPU Performance Prediction of Stencils},
          \small System Seminar, University of Glasgow, UK.}
\cvline{09/2018}
         {\strongHighlight{Invited Talk}:
          \emph{Generating Performance Portable Code with Lift},
         \small \strongHighlight{Shonan Meeting No.134}: Advances in Heterogeneous Computing from Hardware to Software, Japan.}
\cvline{03/2018}
         {\strongHighlight{Invited Talk}:
          \emph{Lift: Code Generation by Rewriting Algorithmic Skeletons},
         \small \strongHighlight{Dagstuhl Seminar 18111} on Loop Optimizations, Schloss Dagstuhl, Germany.}
\cvline{02/2018}
         {\strongHighlight{Invited Talk}:
          \emph{Programming GPUs with Eager Actions and Lazy Views},
         \small Compiler and Architecture Design Group Seminar, University of Edinburgh, UK.}
\cvline{02/2018}
         {Talk: \emph{The Lift Project: Performance Portable Parallel Code Generation via Rewrite Rules},
         \small Formal Analysis, Theory and Algorithms Seminar, University of Glasgow, UK.}
\cvline{11/2017}
         {Talk: \emph{Programming GPUs with Eager Actions and Lazy Views},
         \small System Seminar, University of Glasgow, UK.}
\cvline{10/2017}
         {Talk: \emph{The Lift Project: Performance Portable Parallel Code Generation via Rewrite Rules},
         \small System Seminar, University of Glasgow, UK.}
\cvline{10/2017}
         {\strongHighlight{Invited Talk}:
          \emph{The Lift Project: Performance Portable Parallel Code Generation via Rewrite Rules},
         \small \strongHighlight{Microsoft Research Labs in Cambridge}, UK.}
\cvline{09/2017}
         {\strongHighlight{Invited Talk}:,
          \emph{The Lift Project: Performance Portable Parallel Code Generation via Rewrite Rules},
         \small University of Hull HPC Symposium 2017 at the University of Hull, UK.}
\cvline{07/2017}
         {\strongHighlight{Invited Talk}:,
          \emph{The Lift Project: Performance Portable Parallel Code Generation via Rewrite Rules},
         \small University of Münster, Germany.}
\cvline{06/2017}
         {Talk: \emph{Programming GPUs with Eager Actions and Lazy Views},
         \small Scottish Programming Languages Seminar at the University of the West of Scotland in Paisley, UK.}
\cvline{04/2017}
         {Talk: \emph{Programming GPUs with Eager Actions and Lazy Views},
         \small C++ Edinburgh Meetup in Edinburgh, UK.}
\cvline{02/2017}
         {Talk: \emph{Lift: A Functional Data-Parallel IR for High-Performance GPU Code Generation},
          \small International Symposium on Code Generation and Optimization (CGO) 2017 in Austin, USA.}
\cvline{02/2017}
         {Talk: \emph{Programming GPUs with Eager Actions and Lazy Views},
          \small  International Workshop on Programming Models and Applications for Multicores and Manycores (PMAM) 2017 in Austin, USA.}
\cvline{12/2016}
         {\strongHighlight{Invited Talk}: \emph{The Lift Project: Performance Portable GPU Code Generation via Rewrite Rules},
         Computer Laboratory Systems Research Group Seminar, \strongHighlight{University of Cambridge}, UK.
         }
\cvline{08/2016}
         {\strongHighlight{Invited Talk}:, \emph{Structured Parallel Programming --- From High-Level Functional Expressions to High-Performance OpenCL Code},
         Center for Advanced Electornics Dresden, Dresden University of Technology, Germany.
         }
\cvline{05/2016}
         {\strongHighlight{Invited Talk}:, \emph{Improving Programmability and Performance Portability on Many-Core Processors},
         \small Colloquium of candidates nominated for the \emph{prize for best dissertation} awarded by the German Informatics Society, Schloss Dagstuhl, Germany.}
\cvline{04/2016}
         {\strongHighlight{Invited Talk}: \emph{The lift Project: Performance Portability via Rewrite Rules},
          \small Saarland University, Germany.}
\cvline{01/2016}
         {\strongHighlight{Invited Talk}: \emph{Performance Portable GPU Code Generation},
         \small Imperial College London, UK.}
\cvline{12/2015}
         {Talk: \emph{Functional Programming in C++},
         \small Programming Language Interest Group at Edinburgh University, UK.}
\cvline{10/2015}
         {\strongHighlight{Invited Talk}: \emph{Generating Performance Portable Code using Rewrite Rules},
         \small \strongHighlight{Imperial College London}, UK.}
\cvline{09/2015}
         {Talk: \emph{Generating Performance Portable Code using Rewrite Rules:, From High-Level Functional Expressions to High-Performance OpenCL Code},
         \small International Conference on Functional Programming (ICFP) 2015 in Vancouver, Canada.}
\cvline{06/2015}
         {Talk: \emph{Generating Performance Portable Code using Rewrite Rules},
         \small Scottish Programming Languages Seminar in St.\ Andrews, UK.}
\cvline{05/2014}
         {\strongHighlight{Invited Talk}: \emph{SkelCL\@: High-Level Programming of Multi-GPU
          Systems}, \small Institute for Computational and Applied
          Mathematics, University of Münster, Germany.}
\cvline{05/2014}
         {\strongHighlight{Invited Talk}: \emph{SkelCL\@: High-Level Programming of Multi-GPU
          Systems}, \small Workshop on Fast Data Processing on GPUs in
          Dresden, Germany.}
\cvline{01/2014}
         {Talk: \emph{Extending the SkelCL Library for Stencil
          Computations on Multi-GPU Systems}, \small HiStencils 2014
          workshop in Vienna, Austria.}
\cvline{12/2013}
         {\strongHighlight{Invited Talk}: \emph{SkelCL\@: High-Level Programming of Multi-GPU
          Systems}, \small Research group on elementary particle physics,
          University of Wuppertal, Germany.}
\cvline{07/2013}
         {Talk: \emph{Introducing and Implementing the Allpairs Skeleton for GPU
          Systems}, \small HLPP 2013 workshop in Paris, France.}
\cvline{06/2013}
         {Talk:\emph{High-Level Programming for Medical Imaging on Multi-GPU
          Systems, using the SkelCL Library}, \small ICCS 2013 conference in
          Barcelona, Spain.}
\cvline{08/2012}
       {Talk: \emph{Using the SkelCL Library for High-Level GPU Programming of
        2D Applications}, \small ParaPhrase 2012 workshop held in
        conjunction with Euro-Par 2012 in Rhodes, Greece.}
\cvline{06/2012}
       {Talk: \emph{High-Level Programming for Heterogeneous Systems with
        Accelerators}, \small PDESoft 2012 workshop in Münster, Germany.}
\cvline{05/2012}
       {Talk:\emph{Towards High-Level Programming of Multi-GPU Systems Using
        the SkelCL Library}, \small AsHES 2012 workshop held in
        conjunction with IPDPS 2012 in Shanghai, China.}
\cvline{04/2012}
       {\strongHighlight{Invited talk}: \emph{A Skeleton Library for Heterogeneous
        Multi-/Many-Core Systems}, \small NAIS workshop in Edinburgh, UK.}
\cvline{01/2012}
       {Talk: \emph{Towards a High-Level Approach for Programming Distributed
        Systems with GPUs}, \small COST Action IC0805 (``ComplexHPC'')
        meeting in Timisoara, Romania.}
\cvline{12/2011}
       {\strongHighlight{Invited talk}: \emph{SkelCL --- A High-Level Programming Library for GPU
        Programming}, \small Jülich Supercomputing Centre (JSC), Germany.}
\cvline{05/2011}
       {Talk: \emph{SkelCL --- A Portable Skeleton Library for High-Level
        GPU Programming},
        \small HIPS 2011 workshop held in conjunction with IPDPS 2011 in
        Anchorange, Alaska, USA.}
\cvline{09/2008}
       {\strongHighlight{Invited talk}: \emph{Development of an Online Game as a Student Project},
        \small ITSoftTEAM workshop in Chernihiv, Ukraine.}
